Tutorial for Runing Mouse Bone Marrow Dataset

### 2023-10-16 Demo_marrow_facs.Rmd
changed variable names for results, removed middle color for heatmaps

```{r}
# Construct knn graph
res = Symmetric_KNN_graph(knn = 5, feature_space = feature_space)

A = res$adj_matrix # Adjacency Matrix
W = res$graph # Symmetrized Graph ((A + AT) / 2)

@@

```{r}
# Obtain diffusion KL score
res = fast_calculate_multi_score(W = W, init_state = rho, P_ls = P_ls)

# Check Diffusion KL pattern for several genes
genes = c("Tlr11","Fcnb","Cd79a","4933425H06Rik","Uchl4","Dock11")
genes_label = rep(c("good","bad"),each = 3)
Visualize_score_pattern(res, genes = genes, label_class = genes_label, facet_class = NULL)

# Show result
show_result_lmd(res,n = 10)
```

@@

```{r}
res = LMD(dat,feature_space)
```

@@

```{r}
# Select top1000 genes as local genes
local_gene = show_result_lmd(res, n = 1000)
local_gene = rownames(local_gene)

@@

```{r}
p = pheatmap(as.matrix(dist),
              annotation_col = data.frame(Module = gene_partition), 
              cluster_rows = gene_hree, 
              cluster_cols = gene_hree,
              ann_colors = list(Module = setNames(colorRampPalette(brewer.pal(12, "Paired"))(nlevels(gene_partition)),levels(gene_partition))),
              treeheight_row = 0,
              col=colorRampPalette(c("red","white","blue4"))(99),
              show_colnames = FALSE, 
              show_rownames = FALSE,
              main = paste(distance_method,
                           clustering_method,sep = "-"),
              silent = TRUE )
as.ggplot(p)
```

>>>>

```{r}
# Construct knn graph
knn_result = Symmetric_KNN_graph(knn = 5, feature_space = feature_space)

A = knn_result$adj_matrix # Adjacency Matrix
W = knn_result$graph # Symmetrized Graph ((A + AT) / 2)

@@

```{r}
# Obtain diffusion KL score
score_result = fast_calculate_multi_score(W = W, init_state = rho, P_ls = P_ls)

# Check Diffusion KL pattern for several genes
genes = c("Tlr11","Fcnb","Cd79a","4933425H06Rik","Uchl4","Dock11")
genes_label = rep(c("good","bad"),each = 3)
Visualize_score_pattern(score_result, genes = genes, label_class = genes_label, facet_class = NULL)

# Show result
show_result_lmd(score_result,n = 10)
```

@@

```{r}
lmd_result = LMD(dat, feature_space)
```

@@

```{r}
# Select top1000 genes as local genes
local_gene = show_result_lmd(lmd_result, n = 1000)
local_gene = rownames(local_gene)

@@

```{r}
p = pheatmap(as.matrix(dist),
              annotation_col = data.frame(Module = gene_partition), 
              cluster_rows = gene_hree, 
              cluster_cols = gene_hree,
              ann_colors = list(Module = setNames(colorRampPalette(brewer.pal(12, "Paired"))(nlevels(gene_partition)),levels(gene_partition))),
              treeheight_row = 0,
              col=colorRampPalette(c("red","blue4"))(99),
              show_colnames = FALSE, 
              show_rownames = FALSE,
              main = paste(distance_method,
                           clustering_method,sep = "-"),
              silent = TRUE )
as.ggplot(p)
```
